---
title: "R Notebook"
output: html_notebook
---

```{r}

# libraries ---------------------------------------------------------------

library(ggplot2)
library(dplyr)
library(tidyr)
library(magrittr)
library(tidymodels)

# Model specific libraries
library(discrim)
library(nnet)

```


```{r}

data <- 
  readr::read_delim("../data/Complexo_Bushveld.csv", 
                    delim = ";", 
                    escape_double = FALSE, 
                    trim_ws = TRUE) %>% 
  select(-Date)

## Transforming MaxDepth in categorical
data$MaxDepth <- cut(data$MaxDepth, breaks = c(-Inf,200, 400,Inf), right=FALSE, labels=c("Low", "Middle", "Depth"))
data$MaxDepth <- as.factor(data$MaxDepth)

data <- data %>% na.omit()

```

```{r}

# Train vs test

split <- initial_split(data, prop = 0.8, strata = MaxDepth) # random split
test_data <- testing(split)
train_data <- training(split)

```





## Models

Multinomial regression is used to predict the nominal target variable. In case the target variable is of ordinal type, then we need to use ordinal logistic regression. In this tutorial, we will see how we can run multinomial logistic regression. As part of data preparation, ensure that data is free of multicollinearity, outliers, and high influential leverage points. (https://www.r-bloggers.com/2020/05/multinomial-logistic-regression-with-r/)


Unlike binary logistic regression in multinomial logistic regression, we need to define the reference level. Please note this is specific to the function which I am using from nnet package in R. There are some functions from other R packages where you don’t really need to mention the reference level before building the model.  (https://www.r-bloggers.com/2020/05/multinomial-logistic-regression-with-r/)
# Setting the reference
train$Class <- relevel(train$Class, ref = "adi")

```{r}
# 1. specify the model
# Has no hyperparameters

## Suggested preprocessing:
# 1. dummy
# 2. impute
# 3. decorrelate
# 4. zero variance removed

discrim_linear_MASS_spec <-
  discrim_linear() %>%
  set_engine('MASS') %>%
  set_mode('classification')

## Suggested preprocessing:
# 1. dummy
# 2. impute
# 3. decorrelate
# 4. zero variance removed

discrim_quad_MASS_spec <-
  discrim_quad() %>%
  set_engine('MASS') %>%
  set_mode('classification')

## Suggested preprocessing:
# 1. dummy
# 2. impute
# 3. decorrelate
# 4. zero variance removed

multinom_reg_nnet_spec <-
  multinom_reg(penalty = tune()) %>%
  set_engine('nnet')


# 2. preprocessing 
preprocess <- 
  recipe(MaxDepth ~ . , data = train_data) %>% 
  # keeps this features but they won't be used for fitting
  update_role(ProjectCode, BH_ID, Motherhole,  new_role = "ID") %>%
  step_other(Stratigraphy, threshold = 0.05) %>% 
  # remove variables that have large absolute correlations with other variables
  step_corr(all_numeric_predictors(), threshold = .5) %>% 
  step_normalize(all_numeric_predictors()) %>% 
  step_dummy(all_nominal_predictors()) %>% 
  step_zv(all_predictors())   #will remove columns from the data when the training set data have a single value, 
  #step_nzv(all_predictors())
  
## Preprocessing output
preprocessed_data <- 
  preprocess %>%   
  prep() %>% 
  bake(new_data = NULL)  

  
# 3. Buildworkflow
all_workflows <- 
  workflow_set(
    preproc = list(basic = preprocess),
    models = list(
      lda = discrim_linear_MASS_spec , 
      qda = discrim_quad_MASS_spec , 
      multinorm = multinom_reg_nnet_spec
      )
  )

# 5. Fit control and resamples for crossvalidation
fit_control <- control_resamples(save_pred = TRUE, save_workflow = TRUE)
folds <- vfold_cv(data = train_data, v = 10, repeats = 1)

all_workflows <- 
  all_workflows %>% 
  # tune_grid because of multinomial hyperparameter. Grid search will only apply to this model
  workflow_map(resamples = folds, grid = 20, verbose = TRUE, control = fit_control)


# 5. Fit model with all train data
fit_model <- parsnip::fit(
  object = discrim_linear_MASS_wflow,
  train_data
  ) %>% 
  workflows::extract_fit_parsnip()



```

```{r}

rank_results(all_workflows, rank_metric = "roc_auc",select_best = TRUE)
autoplot(all_workflows, metric = "roc_auc")
autoplot(all_workflows, metric = "accuracy")

```
```{r}

autoplot(all_workflows, metric = "roc_auc", id = "basic_multinorm") 

```

```{r}
multinorm_workflow <- 
  all_workflows %>% 
  extract_workflow("basic_multinorm")

multinorm_fit <- 
  multinorm_workflow %>% 
  finalize_workflow(tibble(penalty = 0.001980769)) %>% 
  fit(data = train_data)

```




```{r}

rank_results(all_workflows, rank_metric = "roc_auc",select_best = TRUE)
autoplot(all_workflows, metric = "roc_auc")
autoplot(all_workflows, metric = "accuracy")

```
```{r}

autoplot(all_workflows, metric = "roc_auc", id = "basic_multinorm") 

```
